\cvheader{Awards \& Honors}

\cventry{National Science Foundation Graduate Research Fellowship}{April 2022}{The NSF GRFP recognizes and supports outstanding graduate students in NSF-supported STEM disciplines who are pursuing research-based master’s and doctoral degrees at accredited US institutions. The five-year fellowship includes three years of financial support including an annual stipend of \$34,000 and a cost of education allowance of \$12,000 to the institution.}{}

\cventry{Astronaut Scholarship}{April 2021}{The Astronaut Scholarship, first established by Mercury 7 astronauts, seeks to identify burgeoning scientific leaders. Astronaut Scholars are chosen based on their ability to move into unknown territory, their motivation, imagination, and exceptional performance in research, and their conveyance of intellectual daring and a genuine desire to positively change the world around them.}{\href{https://go.ncsu.edu/newolfe-astronaut-scholar}{go.ncsu.edu/newolfe-astronaut-scholar}}

\cventry{Goldwater Scholarship}{April 2020}{The Goldwater Scholarship Program, one of the oldest and most prestigious national STEM scholarships in the United States, seeks to identify college sophomores and juniors with exceptional promise of becoming next-generation research leaders, who show
\begin{itemize}
    \item strong commitment to a research career in the natural sciences, mathematics, and engineering,
    \item effective display of intellectual intensity in the sciences, mathematics, and engineering, and
    \item potential for a significant future contribution to research in their chosen field.
\end{itemize}
}{\href{https://lnnk.in/@goldwater-interview}{lnnk.in/@goldwater-interview}}

\cventry{Park Scholarship}{Aug 2018 - May 2022}{NC State's Park Scholarship is a highly selective, full merit scholarship awarded based on outstanding accomplishments and potential in scholarship, leadership, service, and character. Park Scholars participate in a four-year, executive-style leadership academy; diversity training; a year-long service project; and intensive learning laboratories exploring leadership challenges regionally and nationally.}{  \href{https://park.ncsu.edu}{park.ncsu.edu}  }

%\cventry{2nd Place - McCormick Undergraduate Physics Research Symposium}{May 2020}{Won 2nd place for my three-minute, three-slide presentation of my work Characterizing Gravitational Waves from Core-Collapse Supernovae at the NC State McCormick Undergraduate Physics Research Symposium.}{}

%\cventry{Los Alamos National Lab Computational Physics Summer Workshop }{February 2021}{Accepted to the LANL Computational Physics Summer workshop to work on a 10-week summer project with another student and a LANL mentor.}{}

%\cventry{Department of Energy SULI at SLAC}{March 2021}{Accepted to the DOE SULI program at SLAC to study the properties of gamma-ray bursts from type Ib/c supernovae.}{}

\cventry{McCormick Award for Undergraduate Research}{April 2022}{Co-recipient of this award for senior physics undergraduate students, recognizing outstanding research accomplishments.}{}

\cventry{Yusor Abu-Salha Award for Outstanding Community Engagement}{April 2022}{Recipient of this award for senior mathematics undergraduate students who used their time, talents, and intellect to improve their community, recognizing significant accomplishments in the realm of service.}{}

\cventry{1st Place - McCormick Undergraduate Physics Research Symposium}{May 2021}{Awarded for my three-minute presentation on Gravitational Waves from Core-Collapse Supernovae.}{}

\cventry{Math Honors Program at NC State}{September 2020}{}{}
%
\cventry{Phi Beta Kappa}{May 2020}{Invited to join Phi Beta Kappa, the oldest and best-known society for academic excellence and scholarly achievement in the United States, and one of the highest student honors at NC State.}{ \href{https://pbk.org}{pbk.org} }

%\cventry{American Physical Society}{September 2020}{Invited to join the American Physical Society (APS) as a student member, following receipt of the Goldwater Scholarship.}{aps.org}

\cventry{University Scholars Program}{Aug 2018 - May 2022}{The NC State University Scholars Program exposes students to diverse experiences, from local orienteering to talks by National Geographic journalists.}{ \href{https://uhsp.dasa.ncsu.edu}{uhsp.dasa.ncsu.edu} }



%\cventry{Conference Experience for Undergraduates}{October 2019}{Awarded participation in the Conference Experience for Undergraduates (CEU) at the APS Division of Nuclear Physics meeting.}{uwlax.edu/ceu}

